Tulai

### 2023-10-06 paper/paper.qmd
resolve merge conflict

>>>>

```{r}
# SS: get the contributions of each variable to the first two principal components, which we can then use in the text.

res.pca <- PCA(pca_data)

# Contributions of variables to dimension 1 and 2:
contrib_dim1 <- res.pca$var$contrib[, 1]
contrib_dim2 <- res.pca$var$contrib[, 2]
contrib_dim3 <- res.pca$var$contrib[, 3]
contrib_dim4 <- res.pca$var$contrib[, 4]
contrib_dim5 <- res.pca$var$contrib[, 5]

# To view the contributions:
contrib_dim1
contrib_dim2
contrib_dim3
contrib_dim4
contrib_dim5
